PDBF Documentation

### 2015-07-08 Documentation.tex
implemented linking dataText with charts, fixed some bugs

\noindent Macros: \\[3pt]
\verb|\chart[options][queryForOverlay]{queryForPage}| \\
\textbf{Note:} if \verb|queryForOverlay| is omitted the \verb|queryForPage| is used for the overlay.\\
\textbf{Note:} The first column of the query result is used for the x-Axis, all other columns are used for y-Axis.\\[8pt] 
\noindent Options:\\[3pt]
%
Common options\\[4pt]
%
\option
{width}
{Sets the width of the chart.}
{\LaTeX~length}
{No default value. Value must always be set!}

@@

\subsection{Sql}
Example:\\[3pt]
\sql{SELECT * FROM test;}\\[3pt]
%
\noindent Macros: \\[3pt]
\verb|\sql[textForPage]{queryForOverlay}| \\
\textbf{Note:} if \verb|textForPage| is omitted the \verb|queryForOverlay| is used as text for the page.\\[8pt]

@@

\subsection{DataText}
Produce text from sql-statements.\\[3pt]
Example:\\[3pt]
The table ``test'' contains \dataText{SELECT COUNT(*) FROM test;} tuples.\\
The table ``test'' contains the following tuples: \dataText{SELECT * FROM test;}.\\[3pt]
%
\noindent Macros: \\[3pt]
\verb|\dataText{query}| \\[8pt]

@@

>>>>

\noindent Macros: \\[3pt]
\verb|\chart[options][queryForOverlay]{queryForPage}| \\
\textbf{Note:} if \verb|queryForOverlay| is omitted the \verb|queryForPage| is used for the overlay.\\
\textbf{Note:} The first column of the query result is used for the x-Axis, all other columns are used for y-Axis.\\[8pt] 
\noindent Options:\\[3pt]
%
\option
{name}
{Sets the name of this element. This is only useful for linking Elements. See DataText.}
{String}
{\texttt{undefined}}

\option
{width}
{Sets the width of the chart.}
{\LaTeX~length}
{No default value. Value must always be set!}

@@

\subsection{Sql}
Example:\\[3pt]
\sql{SELECT * FROM test;}\\[3pt]
%
\noindent Macros: \\[3pt]
\verb|\sql[options][textForPage]{queryForOverlay}| \\
\textbf{Note:} if \verb|textForPage| is omitted the \verb|queryForOverlay| is used as text for the page.\\[8pt]

@@

\subsection{DataText}
Produce text from sql-statements.\\[3pt]
Example:\\[3pt]
The table ``test'' contains \dataText{SELECT COUNT(*) FROM test;} tuples.\\
The table ``test'' contains the following tuples: \dataText{SELECT * FROM test;}.\\[3pt]
%
\noindent Macros: \\[3pt]
\verb|\dataText[options]{query}| \\[8pt]

@@

\option
{linkTo}
{When this option is set then this DataText and the element with name equal to the value of \texttt{linkTo} are linked. When the cursor is moved above the DataText then in the linked element the specified \texttt{linkSelector} specifies which part of the element is highlighted and annotated with the value of \texttt{linkLabel}.}
{String which value is the name of some other element. \textbf{Currently only chart elements can be used for \texttt{linkTo}.}}
{\texttt{undefined}}

\option
{linkSelector}
{The selector that specifies which part of the \texttt{linkTo} element is highlighted.}
{\texttt{Number}, \texttt{Date} or \texttt{String} depending on the type of the \texttt{linkTo} element. For charts the type depends on the datatype of the xAxis and the value specifies which part of the xAxis is highlighted.}
{\texttt{undefined}}

\option
{linkLabel}
{The text that is displayed near the highlighted area.}
{String}
{\texttt{undefined}}

### 2015-07-08 minimal.tex
added some notes to config. changed documentclass of minimal example.
implemented DataText element
finished dataText
implemented linking dataText with charts, fixed some bugs

\documentclass[10pt]{scrartcl}
\usepackage{PDBF}
\usepackage[a4paper]{geometry}

@@

\begin{document}
\noindent
\sql{SELECT * FROM test;}\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=line]{SELECT * FROM test;}\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=bar]{SELECT * FROM test;}\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=signatureplot]{SELECT b FROM test;}\\[3pt]
\multiplotChart[width=\textwidth, height=0.9\textwidth, xCount=2, yCount=2, yValues={["b", "b*2"]}, xValues={["a > 2", "a <= 2"]}, yFirst]{SELECT a,? FROM test WHERE ?;}\\[3pt]
\pivotTable[width=\textwidth, height=0.5\textwidth, rows={["a"]}, aggregationattribute=b]{SELECT * FROM test;}
\end{document}

>>>>

\documentclass[10pt]{minimal}
\usepackage{PDBF}
\usepackage[a4paper]{geometry}

@@

\begin{document}
\noindent
\sql{SELECT * FROM test;}\\[3pt]
The table ``test'' contains \dataText{SELECT COUNT(*) FROM test;} tuples.\\[3pt]
The following points are linked to the chart below: \dataText[linkTo=testname, linkSelector=2, linkLabel=Value at 2]{SELECT * FROM test WHERE a=2;}, \dataText[linkTo=testname, linkSelector=3, linkLabel=Value at 3]{SELECT * FROM test WHERE a=3;}.\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=line, name=testname]{SELECT * FROM test;}\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=bar]{SELECT * FROM test;}\\[3pt]
\chart[width=\textwidth, height=0.45\textwidth, chartType=signatureplot]{SELECT b FROM test;}\\[3pt]
\multiplotChart[width=\textwidth, height=0.9\textwidth, xCount=2, yCount=2, yValues={["b", "b*2"]}, xValues={["a > 2", "a <= 2"]}, yFirst]{SELECT a,? FROM test WHERE ?;}\\[3pt]
\pivotTable[width=\textwidth, height=0.5\textwidth, rows={["a"]}, aggregationattribute=b]{SELECT * FROM test;}
\end{document}
